Distribution-oblivious Programming with Dish

### 2019-09-21 pldi/draft.tex
Make bib local

Despite these benefits, their development remains different from and significantly more difficult than their centralized counterparts.
Whereas anyone can stitch together a Bash script to compute on a single computer, 
  % domain-experts routinely glue scripts together to process and share data. % without the help of a computing expert.
   scaling out to multiple ones requires expert labor around ``point'' solutions with expensive setups, restricted programming interfaces, and exorbitant composition costs~\cite{maas2014holistic, schwarzkopf2013dios, andromeda:hotos:2015, jonas2017occupy, varghese2018next, nefele:18}.

To understand this sharp contrast, consider calculating frequencies of terms within a set of input files.
For a developer with \emph{one} computer, this is achievable with a short \unix pipeline:

@@

%% Bibliography
\bibliography{../../bib/bib}

>>>>

Despite these benefits, their development remains different from and significantly more difficult than their centralized counterparts.
Whereas anyone can stitch together a Bash script to compute on a single computer, 
  % domain-experts routinely glue scripts together to process and share data. % without the help of a computing expert.
   scaling out to multiple ones requires expert labor around ``point'' solutions with expensive setups, restricted programming interfaces, and exorbitant composition costs~\cite{taurus:14, dios:13, andromeda:2015, pywren:17, futuredata:18, nefele:18}.

To understand this sharp contrast, consider calculating frequencies of terms within a set of input files.
For a developer with \emph{one} computer, this is achievable with a short \unix
pipeline~\cite{bentley1986literate}:

@@

%% Bibliography
\bibliography{./bib}
